%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer {\enskip\cdotp\enskip} IT Consultant} % Job title
    {Devoteam} % Organization
    {Frankfurt, Germany {\enskip\cdotp\enskip} Remote} % Location
    {Since February 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Development of web applications, leveraging cloud technologies, for data visualization with React, MaterialUI, with TypeScript or JavaScript, increasing user satisfaction through the implementation of new functionality.
 \item Transforming client requirements into technical solutions, collaborated in meetings to ensure alignment with stakeholder expectations
     \item Resolving bugs, validating urgent fixes, developing automated tests with Java/Selenium, Cypress, leading to a reduction in system downtime
    \item Implemented Git integration within GitLab CI/CD pipelines to optimize version control and automate deployment workflows.
    \item Contributed to an agile SCRUM environment using Git, Jira, and Confluence to manage tasks and document workflows.
        %\item {Communication with the backend using REST APIs, Google Maps API and implementation of MongoDB database}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Python Programmer {\enskip\cdotp\enskip} System Analyst}
    {ELCA Informatique SA}
    {Granada, Spain {\enskip\cdotp\enskip} Lausanne, Switzerland}
    {Jan. 2021 - Jan. 2022}
    {
      \begin{cvitems}
        \item Automation of business-critical processes and implementation of new functionality in the company-wide production ERP system with Python.
    \item Creating and optimizing VBA scripts to generate business reports.
    \item Querying databases with SQL to ensure data accuracy and integrity.
    \item Conducted business analysis for new features, drafting user stories and acceptance criteria, and coordinating client meetings with stakeholders in Switzerland while collaborating within an international team comprising Spanish, German, and French-speaking colleagues.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer (Internship)}
    {Intel Labs}
    {Karlsruhe, Germany}
    {Aug. 2019 - Jan. 2020}
    {
      \begin{cvitems}
      \item Automotive software development for an open-source simulator 
{\hypersetup{urlcolor=black}\href{https://carla.org/}{CARLA.org}} used for autonomous driving research.
    \item Developed traffic scenarios which describe traffic situations and vehicle behaviors like a lane change with Python.
    \item Debugging, testing, and implementing Parser features.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Engineer (Internship)}
    {BMW M}
    {Munich, Germany}
    {Sep. 2018 - Feb. 2019}
    {
      \begin{cvitems}
        \item Developing a Windows desktop app with C\# to automatically translate bus communication protocols from LIN to CAN and vice versa.
    \item Antenna measurements during test drives in disguised prototype cars.
    \item Coordination of the annual tire change for vehicle fleets, including vehicle bookings, mechanic scheduling, and measurement/technical documentation of wheelbase parameters.
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
