I am writing to express my interest in the \ROLE\ role at \COMPANY\ in \CITY. I graduated with a Master of Science degree in Electrical Engineering and Information Technology in December 2020 and have since been working as a software engineer.

%\lettersection{About Me}
Working in different fields and projects has given me a strong foundation in Python programming and web development with React, TypeScript, and JavaScript. At \companyNow, I worked on projects across industries such as telecommunications, automotive, and energy. My role involved building new applications from the ground up, implementing new features, and fixing bugs while collaborating within agile and international teams and maintaining close contact with stakeholders to ensure alignment with business needs, resulting in optimized solutions and improved business performance. 
Through my past projects, I’ve learned that technology is created by people, for people. This principle guides my approach in developing solutions that are not only technically robust but also user-centric, ensuring they meet real-world needs effectively.

%During my internship at BMW as part of my master's program, I developed an application in C\# for the automatic translation of bus protocols. This reduced the translation process from hours to seconds, enhancing both robustness and reliability.

My goal is to positively impact the team by combining technical expertise with a passion for communication and continuous learning. My GitHub profile reflects my enthusiasm for automation and my curiosity about working with different programming languages. I value simplicity and thoughtful design, principles that lead to maintainable, efficient, and superior solutions. To ensure the best possible outcomes, I place a strong emphasis on testing and discussing solutions with my colleagues to guarantee that software is reliable, robust, and free from defects. Beyond the technical aspects, I thrive in collaborative environments, and working alongside motivated and skilled colleagues and great managers. This has contributed to both my technical and personal growth during my time at \companyNow. If there are any skills in the job description that I am not yet familiar with, I am eager to learn them.

After about three years of working remotely as a software engineer, I am now looking for a new hybrid IT role that will allow me to relocate to \CITY. I am eager to find a role that offers strong career growth, a supportive team environment, and the opportunity to work on agile projects, where I can apply my expertise, learn new skills, and embrace new challenges.

I look forward to hearing from \COMPANY.