%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[10pt, a4paper]{article} 
\usepackage[T1]{fontenc}
\usepackage{fontawesome} 
\usepackage[british]{babel}
\usepackage{ragged2e}
\usepackage{graphicx}        
\usepackage{xcolor}
\usepackage{pifont}
\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{titlesec}
\titlespacing*{\title}{0pt}{-10pt}{10pt}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage[sfdefault]{roboto}
\usepackage[british]{datetime2}
\usepackage{tikz}

\usepackage[
	a4paper, % Paper size
	top=1in, % Top margin
	bottom=1in, % Bottom margin
	left=1in, % Left margin
	right=1in, % Right margin
	%showframe % Uncomment to show frames for debugging purposes
]{geometry}

\setlength{\parindent}{0pt} % Paragraph indentation
\setlength{\parskip}{1em} % Vertical space between paragraphs

\definecolor{cvcolor}{HTML}{333333}


%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
% PERSONAL DATA
%----------------------------------------------------------------------------------------

% Import the personal data
\input{../personal-data.tex}  
%\input{../personal-data-local.tex}

%----------------------------------------------------------------------------------------
% HEADER AND FOOTER CONFIGURATION
%----------------------------------------------------------------------------------------
% Fancy header and footer setup
\pagestyle{fancy}
\fancyhf{} % Clears all header and footer fields

% Remove the default header rule
\renewcommand{\headrulewidth}{0pt}

% Set the footer rule width and color
\renewcommand{\footrulewidth}{1pt} % Footer line thickness
\renewcommand{\footrule}{\color{cvcolor}\hrule} % Set footer line color to cvcolor

% Footer content with colored icons
\fancyfoot[C]{%
    \vspace{0.2cm}\\
    {\Large \textcolor{cvcolor}{\href{mailto:\emailAddress}{\faEnvelope}}} \hspace{0.5cm}
    {\Large \textcolor{cvcolor}{\href{https://wa.me/\phoneNumber}{\faWhatsapp}}} \hspace{0.5cm}
    {\Large \textcolor{cvcolor}{\href{\githubUrl}{\faGithub}}} \hspace{0.5cm}
    {\Large \textcolor{cvcolor}{\href{\linkedinUrl}{\faLinkedinSquare}}}
}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

% Add the colored box with name and address, starting from top-left corner
\begin{tikzpicture}[remember picture, overlay]
    % Draw the blue block at the very top of the page, spanning the full width
    \fill[cvcolor] (current page.north west) rectangle ([yshift=-1.5in]current page.north east); % Blue block with height

    % Add the text inside the blue block, aligned to the left
    \node[anchor=center, text=white] at ([yshift=-0.8in]current page.north -| current page.center) {
        
        \hfill 
\begin{tabular}{@{}p{0.5cm}l@{}}   
 & \textbf{\firstName\ \lastName} \\[0.8ex]
 & \street \\[0.4ex] 
 & \city \\[0.4ex] 
 & \country\\[0.8ex] 
\end{tabular}

    };
\end{tikzpicture}

\vspace{2.5cm}
\bigskip
\bigskip


%----------------------------------------------------------------------------------------
%	ADDRESSEE AND GREETING
%----------------------------------------------------------------------------------------
\newcommand{\COMPANY}{COMPANY}
\newcommand{\ROLE}{ROLE}
\newcommand{\CITY}{CITY}
\newcommand{\COUNTRY}{COUNTRY}

\begin{tabular}{@{}p{0cm}l@{}} 
 & \textbf{\COMPANY} \\[0.8ex] 
 %& STREET \\[0.4ex] 
 & \CITY, \COUNTRY
\end{tabular}

\bigskip % Vertical whitespace

% Date -1 day
%\hfill \today \bigskip\\ 
\hfill \DTMdisplaydate{\year}{\month}{\numexpr\day-1}{.}

% Custom bold, bigger, and underlined title
\noindent \textbf{\underline{Application for \ROLE}}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
To the Esteemed Hiring Team,
\bigskip

I am excited to apply for the \ROLE\ role at \COMPANY\ in \CITY. Since my graduation with a Master of Science degree in Electrical Engineering and Information Technology in December 2020, I have been working as a software engineer with a primary focus on Python programming, web development, and cloud engineering.

Working in different fields and projects has given me a strong foundation in Python programming and web development with React, TypeScript, and JavaScript. At \companynow, I worked on projects across industries such as telecommunications, automotive, and energy. My role involved building new applications from the ground up, implementing new features, and fixing bugs while collaborating in agile and international teams and maintaining close contact with stakeholders to ensure alignment with business needs. During my master's internship at BMW, I developed an application in C\# for the automatic translation of bus protocols. This reduced the translation process from hours to seconds while simultaneously increasing robustness and reliability, significantly optimizing processes.

Beyond my technical expertise, I am adaptable, communicative, and always eager to explore new technologies and share my knowledge. My personal GitHub profile showcases my passion for IT and programming, extending beyond professional projects. I thrive in collaborative environments, and working alongside skilled, motivated colleagues and supportive managers has contributed to my technical and personal growth. Along with enjoying the technical aspects, as a teamplayer, I also appreciate simplicity and thoughtful design, principles that lead to maintainable, efficient, and better solutions. I place a strong emphasis on testing to ensure that software is reliable, robust, and free from defects. If there are any skills in the job description that I am not yet familiar with, I am eager to learn them.

After about three years of working remotely as a software engineer, I am now looking for a new hybrid IT role that will allow me to relocate near \CITY. I am eager to find a role that offers strong career growth, a supportive team environment, and the opportunity to work on agile projects, where I can apply my expertise, learn new skills, and embrace new challenges.

I am looking forward to hearing from \COMPANY. 

\bigskip

Sincerely,

\vspace{20pt}

\firstName\ \lastName

\end{document}